Survey of Cache Oblivious B-trees

### 2011-12-14 paper.tex
Fixing the citations and tweaking layouts

\subsection{Description}
The following subsections describe the structure of the COSB-tree in more detail,
as well as summarize the modifications Bender et al. make to front compression
for COSB-trees.
\subsubsection{General COSB-tree Structure}

@@

\begin{center}
	\includegraphics[width=0.7\columnwidth]{figures/centroidrelayoutexample.pdf}
\end{center}

@@

Before describing the data structures in more detail, we first consider
the concurrency model which is used throughout \cite{BenderFiGi05}.

@@

\begin{figure*}[t]
\begin{center}
    \begin{tabular}{ |   l   |  l     |     l     |     }
    \hline
	Data Structure & Search & Insert / Delete  \\ \hline \hline
	 \textit{Original CO B-tree}  & $O(\log_{B}{N})$ & $O(\log_{B}{N} + \frac{\log^2{N}}{B})$  \\ \hline
	\textit{String CO B-tree}  & $O(1+\log_{B}N+||k||/B)$ &   $O(1+\log_{B}N+\log^{2}N||k||/B)$  \\ \hline
	\textit{Streaming Shuttle Tree}  & $O(\log_{B}{N})$ &  $O(log_{B+1} N / B^{\Theta(1/(loglogB)^2)} + (log^2 N) / B)$  \\ \hline
	\textit{Streaming COLA}  & $O(\log N)$ & $O((\log N) / B)$  \\ \hline
	\textit{Concurrent Exponential CO B-tree} &   $O(\log_B{N} + \log_{\alpha}{\log{B}})$  &   $O(\log_B{N} + \log{\alpha}{\log{B}})$  \\ \hline
	\textit{Concurrent PMA CO B-tree}  & $O(\log_{B}{N} + ({\log{N}})/{B} + 1)$ &   $O(\log_{B}{N} + (\log^2{N})/{B} + 1)$  \\ \hline
    \end{tabular}
    \caption{A summary of the surveyed CO B-trees. The bounds are in terms of the number of memory transfers. The bounds for \textit{Concurrent Exponential CO B-tree} are in expectation only.}
    \label{fig:table}
\end{center}
\end{figure*}

@@

\vfill

@@

>>>>

\subsubsection{General COSB-tree Structure}

@@

\begin{center}
	\includegraphics[width=0.8\columnwidth]{figures/centroidrelayoutexample.pdf}
\end{center}

@@

Before describing the data structures in more detail, we first consider
the concurrency model which is used in \cite{BenderFiGi05}.

@@

\begin{figure*}[t]
\begin{center}
    \begin{tabular}{ |   l   |  l     |     l     |     }
    \hline
	Data Structure & Search & Insert / Delete  \\ \hline \hline
	 \textit{Original CO B-tree}  & $O(\log_{B}{N})$ & $O(\log_{B}{N} + \frac{\log^2{N}}{B})$  \\ \hline
	\textit{String CO B-tree}  & $O(1+\log_{B}N+||k||/B)$ &   $O(1+\log_{B}N+\log^{2}N||k||/B)$  \\ \hline
	\textit{Streaming Shuttle Tree}  & $O(\log_{B}{N})$ &  $O(log_{B+1} N / B^{\Theta(1/(loglogB)^2)} + (log^2 N) / B)$  \\ \hline
	\textit{Streaming COLA}  & $O(\log N)$ & $O((\log N) / B)$  \\ \hline
	\textit{Concurrent Exponential CO B-tree} &   $O(\log_B{N} + \log_{\alpha}{\log{B}})$  &   $O(\log_B{N} + \log{\alpha}{\log{B}})$  \\ \hline
	\textit{Concurrent PMA CO B-tree}  & $O(\log_{B}{N} + ({\log{N}})/{B} + 1)$ &   $O(\log_{B}{N} + (\log^2{N})/{B} + 1)$  \\ \hline
    \end{tabular}
    \caption{A summary of the surveyed CO B-trees. The bounds are in terms of the number of memory transfers. The bounds for \textit{Concurrent Exponential CO B-tree} are in expectation only.}
    \label{fig:table}
\end{center}
\vspace{-0.2in}
\end{figure*}

@@

@@

\vspace{0.15in}
